Biden Projected to Win in the 2024 US Presidential Election

### 2024-03-15 paper/paper.qmd
made changes to the discussion section

In the graph showcasing different regions and their voting for biden, we noticed that
This is similar to the findings in https://www.brookings.edu/articles/forecasting-the-presidential-election-what-can-
we-learn-from-the-models/
that address the same prediction for 2024. Our model and the article predict that states that support Trump are
from the middle and Midwest parts of the US, whereas coastal states and the Northeast tend to vote for Biden.
Historically, rural, conservative-leaning towns with strong cultural ties to traditional values and industries like
manufacturing and agriculture have defined the middle and Midwest regions of the United States.
These areas frequently support gun rights, minimal government intrusion, and religious liberty—issues that are strongly
aligned with the agenda of the Republican Party, which Trump advocated. In contrast, the Northeast and coastline states,
which are renowned for their progressive views on culture, urban facilities, and diverse populations, have historically tended toward more liberal policies and social ideals that are more in line with the Democratic Party platform, which Biden advocated.

We also created a graph highlighting different age groups and what their voting opinions are. We noticed that
the youngest group of voters (age 18-24). The emphasis on social justice and LGBTQ+ rights among the younger generation may be the cause of this difference. Since there are undoubtedly more young people who identify as sexual minorities, there is a trend for them to support Biden and the Democratic Party. We also noticed that the older generation i.e individuals of age group higher than 60 years old were inclined to voting for Biden as well.
National security and conservative principles, which are frequently connected to the Republican Party, may have an impact on the elder generation.

Lastly, our third variable of study was Sex. We noticed a slight bias towards the democratic party from the females than the male gender. Women are predicted to vote for the democratic party 0.6 times more than men.
Studies have consistently demonstrated that there is a gender difference in political ideology, with women generally favoring liberal or progressive policies over those of males. https://www.pewresearch.org/politics/2023/07/12/voting-patterns-in-the-2022-elections/#:~:text=In%20the%202022%20midterms%2C%2054,2022%20while%2051%25%20favored%20Democrats.
This discrepancy is sometimes linked to the fact that women prioritize issues more than men do, with women giving social welfare, healthcare, education, and reproductive rights—all of which are more in line with the Democratic Party program. With its focus on women's rights, healthcare reform, and inclusivity, Biden's campaign may have connected more deeply with female voters, resulting in higher levels of support.

## Comparative Analysis:
Our findings align with existing literature on electoral behavior, which underscores the significance of demographic variables in shaping voter preferences. While our study offers insights into the inclination towards voting for Biden, it is important to contextualize our findings within the broader landscape of political science research. https://projects.economist.com/us-2020-forecast/president/how-this-works

@@

## Contributions to Knowledge: (Need to edit this)
By focusing our analysis on specific demographic variables, we contributed to a deeper understanding of the underlying determinants shaping electoral outcomes. Our study corroborates existing literature suggesting that demographic factors such as age, income, education, and geographic location play pivotal roles in influencing voter preferences. 
(https://projects.economist.com/us-2020-forecast/president/how-this-works)
Moreover, our utilization of post-stratification techniques allowed for a more granular examination of voting behavior, offering insights into the heterogeneity of voter sentiment across different demographic groups.

## Weaknesses and Limitations: (Need to edit this)

@@

Additionally, while we focused on key demographic variables, other influential factors such as political ideology and campaign messaging were not fully accounted for in our model. This means that our research has the inaccuracy of Incomplete Variable Consideration.

>>>>

In the graph showcasing different regions and their voting for biden, we noticed that
This is similar to the findings in [@James_2016] that address the same prediction for 2024. Our model and the
article predict that states that support Trump are from the middle and Midwest parts of the US, whereas coastal states
and the Northeast tend to vote for Biden.

Historically, rural, conservative-leaning towns with strong cultural ties to traditional values and industries like
manufacturing and agriculture have defined the middle and Midwest regions of the United States.
These areas frequently support gun rights, minimal government intrusion, and religious liberty—issues that are strongly
aligned with the agenda of the Republican Party, which Trump advocated. In contrast, the Northeast and coastline states,
which are renowned for their progressive views on culture, urban facilities, and diverse populations, have historically
tended toward more liberal policies and social ideals that are more in line with the Democratic Party platform, which Biden advocated.

We also created a graph highlighting different age groups and what their voting opinions are. We noticed that
the youngest group of voters (age 18-24). The emphasis on social justice and LGBTQ+ rights among the younger generation
may be the cause of this difference[@Brownstein_2023]. Since there are undoubtedly more young people who identify as sexual minorities,
there is a trend for them to support Biden and the Democratic Party. We also noticed that the older generation i.e
individuals of age group higher than 60 years old were inclined to voting for Biden as well.
National security and conservative principles, which are frequently connected to the Republican Party,
may have an impact on the elder generation.

Lastly, our third variable of study was Sex. We noticed a slight bias towards the democratic party from the females than
the male gender. Women are predicted to vote for the democratic party 0.6 times more than men.
Studies have consistently demonstrated that there is a gender difference in political ideology, with women generally
favoring liberal or progressive policies over those of males.[@Igielnik_2021]
This discrepancy is sometimes linked to the fact that women prioritize issues more than men do, with women giving social
welfare, healthcare, education, and reproductive rights—all of which are more in line with the Democratic Party program.
With its focus on women's rights, healthcare reform, and inclusivity, Biden's campaign may have connected more
deeply with female voters, resulting in higher levels of support.

## Comparative Analysis:
Our findings align with existing literature on electoral behavior, which underscores the significance of demographic
variables in shaping voter preferences. While our study offers insights into the inclination towards voting for Biden,
it is important to contextualize our findings within the broader landscape of political science research.[Gelman]

@@

## Contributions to Knowledge:
By focusing our analysis on specific demographic variables, we contributed to a deeper understanding of the underlying
determinants shaping electoral outcomes. Our study corroborates existing literature suggesting that demographic factors
such as age, income, education, and geographic location play pivotal roles in influencing voter preferences. [@Gelman]
Moreover, our utilization of post-stratification techniques allowed for a more granular examination of voting behavior,
offering insights into the heterogeneity of voter sentiment across different demographic groups.

## Weaknesses and Limitations:

@@

Additionally, while we focused on key demographic variables, other influential factors such as political ideology and
campaign messaging were not fully accounted for in our model. This means that our research has the inaccuracy of
Incomplete Variable Consideration[@Funakoshi_2020].
